I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-19 Paper/Paper_noProof.tex
typo

We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
The bounds for nodes of the second layers are computed exactly. 
Let $d$ be a neuron of the third layer.
We keep the previous evaluation for ranking nodes in the previous (second) layer. 
Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$. We thus define:
\vspace{-0.2cm}
$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
\vspace{-0.2cm}

>>>>

We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer.
The bounds for nodes of the first two layers are computed exactly. 
Let $d$ be a neuron of the third layer.
We keep the previous evaluation for ranking nodes in the previous (second) layer. 
Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ from the first layer to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$. We thus define:
\vspace{-0.2cm}
$$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min( weight(abcd),weight(ab'c'd))$$ 
\vspace{-0.2cm}
